---
title       : Synthesis Test on JT1 2014
subtitle    : 
author      : Luis Razo
job         : 
framework   : revealjs      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

--- .class #id .background "#006600" 
## Synthesis Test on JT1 2014

Luis Razo

`r Sys.Date()`

--- .class #id .background "#006600" 

## Synopsis

The present analysis consider the most relevant test that have been performed over the JT1 system evaluating the performance, we consider the date of the test and the evolution of the results on the time.

--- .class #id 

## Base scenario

```{r echo=FALSE, }

path        <- ".\\test\\TestPlanner\\synopsis\\"
filePatrn   <- c("Test_","_WS_on_users_","_","_","_autounset_","_",".csv")
systems     <- c("JT1")
usersTo     <- 1
usersIncr   <- 1
users       <- c(100)
ramups      <- c(500)
times       <- c(45)
requests    <- 40
models      <- c("KB_GCR_NW_CB")
versions    <- c("141023.0")
setDefaults <- c("true")
autounsets  <- c("true")
tempRequest <- "2"

quantities <- c(20)
```
The scenario is composed by 40 setCstic. 


Data acquisition


+ Using JMeter

- Systems:              `r systems`
    
- Model(alias):         `r models`

- Version:              `r versions`

- AutoUnset:            `r autounsets`

- defaultValues:        `r setDefaults`



--- .class #id 

## Base scenario

+ setCstic using the following parameters at each request:

```{r showtable1, results="asis", echo=FALSE}
library(xtable)
setwd(".")
fileName <- ".\\testScenario.csv"
scenario <- read.csv(fileName, sep = ";", colClasses = c("character","character","character"))
xscenario <- xtable(scenario[1:12,])
print(xscenario, type = "html", row.names=F)
```

--- .class #id 

## Base scenario

```{r showtable1x, results="asis", echo=FALSE}
xscenario <- xtable(scenario[13:25,])
print(xscenario, type = "html", row.names=F)

```

--- .class #id 

## Base scenario

```{r showtable1y, results="asis", echo=FALSE}
xscenario <- xtable(scenario[25:37,])
print(xscenario, type = "html", row.names=F)

```

--- .class #id 

## Base scenario

```{r showtable1z, results="asis", echo=FALSE}
xscenario <- xtable(scenario[37:40,])
print(xscenario, type = "html", row.names=F)

```


--- .class #id 

## Base scenario

+ deleteConfig at the end.


--- .class #id 

## Results all tests

```{r showtable2, echo=FALSE, cache=TRUE}
fileNames <- list.files(path = path)
#fileNames <- paste(path,list.files(path = path),sep="")
#df <- data.frame(file.info(fileNames)$mtime, fileName )
table <- c()
for(fileName in fileNames){
    fileToRead <- paste(path,fileName,sep="")
    if(file.exists(fileToRead)){
        ttable <- read.csv(fileToRead,header = F)        
        ttable[[1]] <- as.POSIXct(as.numeric(substring(ttable[[1]],1,nchar(ttable[[1]])-3)), origin="1970-01-01")
        colnames(ttable) <- c("StartTime","SampleTimeMS","RequestNumber","HTTPResponse","Response","ThreadName",
                              "HTTPText","Status","Bytes","Latency")
        
        totalRows <- nrow(ttable)
        ttable <- ttable[ttable$SampleTimeMS < 60000,]
        rowsError <- totalRows - nrow(ttable)
        noclicks <- nrow(ttable)
        
        x <- aggregate(. ~ RequestNumber, data=ttable[c(2,3,9)], mean)
        
        
        
        x$min <- aggregate(. ~ RequestNumber, data=ttable[c(2,3)], min)[[2]]
        x$max <- aggregate(. ~ RequestNumber, data=ttable[c(2,3)], max)[[2]]
        x$sd <- aggregate(. ~ RequestNumber, data=ttable[c(2,3)], sd )[[2]]
        #x$totalreq <- agregate(. ~ RequestNumber, data=ttable[c(2,3)], sum )[[2]]
        
        for( i in 1:length(x$sd))
        if(is.na(x$sd[i])){
            x$sd[i] <- 0
        }
        
        x[[1]] <- as.numeric(x[[1]])
        x[[2]] <- x[[2]] 
        #x$createTime <- file.info(fileName)$mtime
        x$fileName <- fileName
        #strsplit(x = fileName,"[_]")
        x$createTimeX <- ttable$StartTime[1]
        x$totalClicks <- nrow(ttable)
        x$rowsError <- rowsError
        
         if(grepl("autounset",fileName)){            
            x$users <- gsub("Test_JT1_(\\d{1,4})_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_autounset_\\w{4,5}_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$model <- gsub("Test_JT1_\\d{1,4}_(KB_.*)\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_autounset_\\w{4,5}_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$version <- gsub("Test_JT1_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_(\\d{6}\\.\\d{1})_autounset_\\w{4,5}_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$defaultVals <- gsub("Test_JT1_\\d{1,4}_KB_.*\\.SIMPLE_(\\d{1,2})_\\d{1,2}_\\d{6}\\.\\d{1}_autounset_\\w{4,5}_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$modelAlias <- gsub("Test_JT1_\\d{1,4}_(KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2})_\\d{6}\\.\\d{1}_autounset_\\w{4,5}_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$autounset <- gsub("Test_JT1_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_autounset_(\\w{4,5})_\\d{8}_\\d{6}_\\d{1,4}.csv", "\\1", c(fileName))
            x$ramup <- gsub("Test_JT1_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_autounset_\\w{4,5}_\\d{8}_\\d{6}_(\\d{1,4}).csv", "\\1", c(fileName))
            x$times <- "unknown"
            x$setDefaults <- "unknown"
        }else{
            x$users <- gsub("Test_JT1_(\\d{1,4})_\\d{1,4}_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$model <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_(KB_.*)\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$version <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_(\\d{6}\\.\\d{1})_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$modelAlias <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_(KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2})_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$autounset <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_(\\w{4,5})_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$setDefaults <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_(\\w{4,5})_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$ramup <- gsub("Test_JT1_\\d{1,4}_(\\d{1,4})_\\d{1,4}_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$times <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_(\\d{1,4})_KB_.*\\.SIMPLE_\\d{1,2}_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
            x$defaultVals <- gsub("Test_JT1_\\d{1,4}_\\d{1,4}_\\d{1,4}_KB_.*\\.SIMPLE_(\\d{1,2})_\\d{1,2}_\\d{6}\\.\\d{1}_\\w{4,5}_\\w{4,5}_{0,1}\\d{0,2}.csv", "\\1", c(fileName))
        }
        x$diffTimeMins <- difftime(ttable[nrow(ttable),1], ttable[1,1],units = "mins")
        x$confPerHour <- (x$totalClicks/41) * 60 / as.numeric(difftime(ttable[nrow(ttable),1], ttable[1,1],units = "mins"))
        x$fileData <- paste("Users: ", x$users, "\n\n Model: ",x$model,"\n\t Version: ",x$version, "\n\n  defaultValues: ", x$defaultVals, "\n\n autounset: ", x$autounset, "\n\t setDefaults: ", x$setDefaults, "\n\n ramup: ", x$ramup, "\n\t times: ", x$times, "\n\n Errors: ", x$rowsError,"\n\t Clicks: ", x$totalClicks,"\n\n Configurations: ", round(as.numeric((x$totalClicks/41)),0) ,"\n\nThe test started at ", ttable[1,1] ," and finished at ", ttable[nrow(ttable),1],"\n\n","Therefore the total duration was around ", round(x$diffTimeMins,0)," minutes.\n\n","The number of configurations by hour was around ", round(x$confPerHour,0)," \n\n", sep="")
        #x$system  <- sys          
        #x$model   <- model
        #x$version <- version
        #x$users   <- user
        ##x$time    <- time
        #x$setDefault <- setDefault
        #x$autounset  <- autounset
        #x$ramup  <- ramup
        #x$model <- model
        #x$version <- version
        #x$autounset <- autounset
        table <- rbind(table,x)                                
    }
    
}
 
```

```{r, fig.width= 12, fig.height= 7, echo=FALSE, warning=F,results='asis'}
    library(grid)    
    library(ggplot2)
    library(reshape2)
    library(ggthemes)
    library(scales)
    

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r, echo=FALSE, warning=F}
table <- table[order(table$createTimeX),]
table$createTimeF <- as.factor(table$createTimeX)
table$fileNameF <- as.factor(table$fileName)
table$confPerHourF <- as.factor(round(table$confPerHour,0))
table$usersF <- as.factor(as.numeric(table$users))
table$diffTimeMinsF <- as.factor(round(table$diffTimeMins,0))
table$totalClicksF <- as.factor(as.numeric(table$totalClicks))
table$totalConf <- as.factor(round(as.numeric(table$totalClicks/41),0))
```

```{r, echo=FALSE, warning=F}
table$fileDate <- paste(table$fileNameF," \n ",table$createTimeF,sep = "")
write.csv(table,"table.csv")
colours <- scales::hue_pal()(length(unique(table$fileDate)))
#colours <- c(colours,scales::hue_pal()(length(unique(table$fileDate))))
cols <- c("st" = "black","max"="green","min"="orange","15"="red","30"="blue","sd"="purple")
```

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=SampleTimeMS,x=RequestNumber,colour=createTimeF),data=table) + geom_line(aes(group=createTimeF),size=0.75,)  + xlim(0,41) + ylim(0,6000) +
    ylab("Sample Time (ms)") + xlab("Request Number") + guides(col=guide_legend(ncol=5)) + ggtitle("All Tests") + scale_color_manual(name = "Test date",values = colours) + guides(fill=guide_legend(title="Request Number")) + theme(legend.position="bottom") 
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=confPerHourF,x=createTimeF,colour=createTimeF),data=table) + geom_point(aes(colour = createTimeF)) +
    ylab("Conf/Hour") + xlab("Date of Test") + ggtitle("Conf/Hour per Test") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=5)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Test date")
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=confPerHourF,x=usersF,colour=createTimeF),data=table) + geom_point(aes(colour = createTimeF)) +
    ylab("Conf/Hour") + xlab("Num Users") + ggtitle("Conf/Hour per Num of Users (Color by test date)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=5)) + scale_colour_hue(name ="Test date")
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=confPerHourF,x=diffTimeMinsF,colour=createTimeF),data=table) + geom_point(aes(colour = createTimeF)) +
    ylab("Conf/Hour") + xlab("Duration (mins)") + ggtitle("Conf/Hour per Test Duration (Color by test date)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=5)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Test date")
```


--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=confPerHourF,x=diffTimeMinsF,colour=usersF),data=table) + geom_point(aes(colour = usersF)) +
    ylab("Conf/Hour") + xlab("Duration (mins)") + ggtitle("Conf/Hour per Test Duration (Color by Num Users)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=6)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Num of Users")
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=confPerHourF,x=totalClicksF,colour=createTimeF),data=table) + geom_point(aes(colour = createTimeF)) +
    ylab("Conf/Hour") + xlab("Num clicks") + ggtitle("Conf/Hour per Num of Clicks (Color by test date)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=6)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Test date")
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=diffTimeMinsF,x=totalConf,colour=usersF),data=table) + geom_point(aes(colour = usersF)) +
    ylab("Duration (mins)") + xlab("Num Confs") + ggtitle("Duration per Num of Confs (Color by Num Users)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=6)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Num of Users")
```

--- .class #id 

## Results all tests

```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
ggplot(aes(y=usersF,x=diffTimeMinsF,colour=confPerHourF),data=table) + geom_point(aes(colour = confPerHourF)) +
    ylab("Num Users") + xlab("Duration (mins)") + ggtitle("Num Users per Test Duration (Color by Conf/Hour)") + theme(legend.position="bottom") + guides(col=guide_legend(ncol=6)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_hue(name ="Conf/Hour")

```


```{r, echo=FALSE, warning=F,results='asis', fig.width= 12, fig.height= 7}
colour <- 0
counter <- 0
lenRes <- length(unique(table$fileDate)) * 2
for( value in unique(table$fileDate) ){
    currentData <- table[table$fileDate == value,]
    colour <- colour + 1
    g <- ggplot(aes(y=SampleTimeMS,x=RequestNumber,colour=colours[colour]),data=currentData) + xlim(0,41) + 
    ylab("Sample Time (ms)") + xlab("Request Number") + guides(fill=guide_legend(title="Request Number")) +  theme(plot.title = element_text(size = rel(0.75))) + scale_color_manual(name = "",values = c(colours[colour], "sampleTime"= colours[colour],"max"="green","min"="orange","sd"="purple"))
    
    pnormal <- g + labs(title = value) + geom_line(aes(group=fileNameF, colour = "sampleTime"), size=0.75) + ylim(0,6000) + theme(legend.position="none")
    
    pmaxmin <- g + labs(title = "Max & min limit values") + geom_line(aes(group=fileNameF, colour = "sampleTime"), size=0.75) + ylim(0,max(currentData$max)) +  geom_line(aes(x = RequestNumber, y = max,colour="max")) + geom_line(aes(x = RequestNumber, y = min,colour="min")) + theme(legend.position="bottom") + guides(col=guide_legend(nrow=1)) 

    psd <- g + labs(title = "+/- Standard Deviation") + geom_line(aes(group=fileNameF, colour = "sampleTime"), size=0.75) + ylim(0,max(currentData$SampleTime + currentData$sd))  + geom_line(aes(x = RequestNumber, y = SampleTimeMS - sd ,colour="sd")) +geom_line(aes(x = RequestNumber, y = SampleTimeMS + sd ,colour="sd")) + theme(legend.position="bottom") + guides(col=guide_legend(nrow=1))
    
    counter <- counter + 1
    cat("\n\n--- .class #id \n")
    cat(paste("\n\n## Test case ",currentData$createTimeF[1]," \n\n",sep=""))
    cat(currentData$fileData[1])    
    
    counter <- counter + 1
    cat("\n\n--- .class #id \n")
    cat(paste("\n\n## Test case ",currentData$createTimeF[1]," \n\n",sep=""))
    print(pnormal)
    
    counter <- counter + 1
    cat("\n\n--- .class #id \n")
    cat(paste("\n\n## Test case ",currentData$createTimeF[1]," \n\n",sep=""))
    #cat(paste("\n\n## Results (",counter,"/",lenRes,")\n\n",value,sep=""))
    multiplot(pmaxmin, psd, cols=2)
}
```
